\chapter*{Acknowledgments}

I have many people to thank in this dissertation. It's been a long journey,
but I've met and learned from so many awesome people along the way. It goes without
saying that this dissertation was the result of work and mentorship from many people.

First and foremost,
I want to thank my advisors, Nickolai Zeldovich and James Mickens. I've learned so much
from the both of them along the way. I want to thank them for providing me
the independence and support to work on ideas that I thought were interesting.

Next, I want to thank my collaborators, Vinod Vaikuntanathan, Shafi Goldwasser,
Matei Zaharia, and Catherine Yun. I also want to thank my research family at MIT,
specifically Jen Gong, Amy Zhao, Amy Ousterhout, Tej Chajed, Guha Balakrishnan,
Jon Gjenset, David Lazar, Taesoo Kim, Xi Wang, Haogong Chen, Neha Narula, Ravi Netravali, Silas Boyd-Wickizer,
Jean Yang, and everyone else in the PDOS group. I've learned a lot from you, and you
made my time at MIT very enjoyable.

I want to thank my friends who have provided me great advice and support along the way.
I want to thank everyone I met at Rough Draft Ventures, all the mentors at
Highland Capital and Cybersecurity Factory, and my friends in Sidney Pacific. Your
friendship has allowed me to stay grounded during my PhD. 

Finally, I want to thank my parents for allowing me to live on a different
coast for the past six years. They have always been supportive of my life choices
and adventures.

\asterism

%This research was supported in part by NSF awards CNS-1053143 and
%CCF-1253229, and by the CSAIL cybersecurity initiative.

This work was
partially supported by an NSF Graduate Research Fellowship
(Grant No. 2013135952) and by NSF awards
CNS-1053143, CNS-1413920, CNS-1350619, 
and CNS-1414119. \\

The dissertation incorporates and extends work published
in the following papers:

\begin{quote}

  Frank Wang, James Mickens, and Nickolai Zeldovich.
  \newblock Veil: Private Browsing Semantics Without Browser-side Assistance.
  \newblock In \emph{Proceedings of Network and Distributed System Security Symposium (\mbox{NDSS})},
  2018.
  
  Frank Wang, Catherine Yun, Shafi Goldwasser, Vinod Vaikuntanathan, and Matei Zaharia.
  \newblock Splinter: Practical Private Queries on Public Data.
  \newblock In \emph{Proceedings of Networked Systems Design
  	and Implementation (\mbox{NSDI})}, 2017.
  
\end{quote}
